An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-17 paper.tex
Added NSF acknowledgement, closes #86.

\section*{Grant Information}
The work was partially funded by the State of Ohio Third Frontier Commission
through the Wright Center for Sensor Systems Engineering (WCSSE).

>>>>

\section*{Grant Information}
The work was partially funded by the State of Ohio Third Frontier Commission
through the Wright Center for Sensor Systems Engineering (WCSSE) and by the
National Science Foundation under Grant No. 1344954.
